```{r}
library(caTools)
library(caret)
library(tidyr); library(dplyr)
library(tidyr);library(tidyverse);library(forecast);library(forcats);library(stringr)
nn <- read.csv("C:/Users/josh1/Downloads/Touch2.csv")
nn
airbnb <- nn
summary(nn)
names(nn)

names(nn)

```

```{r, result = "hide"}
library(tidyverse)
library(ggthemes)
library(GGally)
library(ggExtra)
library(caret)
library(glmnet)
library(corrplot)
library(leaflet)
library(kableExtra)
library(RColorBrewer)
library(plotly)
```

```{r}
th <- theme_fivethirtyeight() + theme(axis.title = element_text(), axis.title.x = element_text()) # global theme for ggplot2 objects
set.seed(252)
airbnb <- read.csv("C:/Users/josh1/Downloads/Touch3.csv", 
                   encoding="UTF-8", stringsAsFactors = F, na.strings = c(""))
```

```{r}
head(airbnb) %>% kable() %>% kable_styling()
```

```{r}
names_to_factor <- c("host_name", "neighbourhood_group", "neighbourhood", "room_type")
airbnb[names_to_factor] <- map(airbnb[names_to_factor], as.factor)
airbnb$host_name <-as.factor(airbnb$host_name)
airbnb$neighbourhood_group <-as.factor(airbnb$neighbourhood_group)
airbnb$neighbourhood <-as.factor(airbnb$neighbourhood)
airbnb$room_type <-as.factor(airbnb$room_type)
class(airbnb$room_type)
```

```{r}
airbnb[c("last_review")] <- airbnb[c("last_review")] %>% map(~lubridate::ymd(.x))
```

```{r, result = "hide"}
glimpse(airbnb)
```
```{r}
missing_airbnb <- airbnb %>% summarise_all(~(sum(is.na(.))/n()))
missing_airbnb <- gather(missing_airbnb, key = "variables", value = "percent_missing")
missing_airbnb <- missing_airbnb[missing_airbnb$percent_missing > 0.0, ] 
ggplot(missing_airbnb, aes(x = reorder(variables, percent_missing), y = percent_missing)) +
geom_bar(stat = "identity", fill = "red", aes(color = I('white')), size = 0.3)+
xlab('variables')+
coord_flip() + 
th  +
  ggtitle("Missing Data") +
  xlab("Column name") +
  ylab("Percentage missing") +
  annotate("text", x = 1.5, y = 0.1,label = "host_name and name have less than 0.001\n percentage missing", color = "slateblue", size = 5)
```
```{r}
ggplot(airbnb, aes(price)) +
  geom_histogram(bins = 30, aes(y = ..density..), fill = "purple") + 
  geom_density(alpha = 0.2, fill = "purple") +
  th +
  ggtitle("Distribution of price",
          subtitle = "The distribution is very skewed") +
  theme(axis.title = element_text(), axis.title.x = element_text()) +
  geom_vline(xintercept = round(mean(airbnb$price), 2), size = 2, linetype = 3)
```
```{r}
ggplot(airbnb, aes(price)) +
  geom_histogram(bins = 30, aes(y = ..density..), fill = "purple") + 
  geom_density(alpha = 0.2, fill = "purple") +
  th +
  ggtitle("Transformed distribution of price",
          subtitle = expression("With" ~'log'[10] ~ "transformation of x-axis")) +
  #theme(axis.title = element_text(), axis.title.x = element_text()) +
  geom_vline(xintercept = round(mean(airbnb$price), 2), size = 2, linetype = 3) +
  scale_x_log10() +
  annotate("text", x = 1800, y = 0.75,label = paste("Mean price = ", paste0(round(mean(airbnb$price), 2), "$")),
           color =  "#32CD32", size = 8)

```
```{r}
airbnb_nh <- airbnb %>%
  group_by(neighbourhood_group) %>%
  summarise(price = round(mean(price), 2))


ggplot(airbnb, aes(price)) +
  geom_histogram(bins = 30, aes(y = ..density..), fill = "purple") + 
  geom_density(alpha = 0.2, fill = "purple") +
  th +
  ggtitle("Transformed distribution of price\n by neighbourhood groups",
          subtitle = expression("With" ~'log'[10] ~ "transformation of x-axis")) +
  geom_vline(data = airbnb_nh, aes(xintercept = price), size = 2, linetype = 3) +
  geom_text(data = airbnb_nh,y = 1.5, aes(x = price + 1400, label = paste("Mean  = ",price)), color = "darkgreen", size = 4) +
  facet_wrap(~neighbourhood_group) +
  scale_x_log10() 
```

```{r}
airbnb %>% filter(price >= mean(price)) %>% group_by(neighbourhood_group, room_type) %>% tally %>% 
  ggplot(aes(reorder(neighbourhood_group,desc(n)), n, fill = room_type)) +
  th +
  xlab(NULL) +
  ylab("Number of objects") +
  ggtitle("Number of above average price objects",
          subtitle = "Most of them are entire homes or apartments") +
           geom_bar(stat = "identity")
```
```{r}
ggplot(airbnb, aes(x = room_type, y = price)) +
  geom_boxplot(aes(fill = room_type)) + scale_y_log10() +
  th + 
  xlab("Room type") + 
  ylab("Price") +
  ggtitle("Boxplots of price by room type",
          subtitle = "Entire homes and apartments have the highest avg price") +
  geom_hline(yintercept = mean(airbnb$price), color = "purple", linetype = 2)
```
```{r}
ggplot(airbnb, aes(x = property_type, y = price)) +
  geom_boxplot(aes(fill = property_type)) + scale_y_log10() +
  th + 
  xlab("Property Type") + 
  ylab("Price") +
  ggtitle("Boxplots of price by Property type",
          subtitle = "Entire homes and apartments have the highest avg price") +
  geom_hline(yintercept = mean(airbnb$price), color = "purple", linetype = 2)
```

```{r}
data %>%
  ggplot(aes(price, fill = neighbourhood_group_cleansed)) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 20) +
  scale_x_log10(labels = scales::dollar_format()) +
  labs(fill = NULL, x = "price per night")
```
```{r}
 data %>%
  ggplot(aes(price, fill = host_since_lev)) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 20) +
  scale_x_log10(labels = scales::dollar_format()) +
  labs(fill = NULL, x = "price per night")
```
```{r}
data %>%
  ggplot(aes(price, fill = neighbourhood_group_cleansed)) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 20) +
  scale_x_log10(labels = scales::dollar_format()) +
  labs(fill = NULL, x = "price per night")
```

```{r}
data %>%
  ggplot(aes(price, fill = room_type)) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 20) +
  scale_x_log10(labels = scales::dollar_format()) +
  labs(fill = NULL, x = "price per night")
```

```{r}
airbnb %>% arrange(desc(price)) %>% top_n(10) %>% select(- host_name, -name) %>%  
  ggplot(aes(x = price, fill = neighbourhood_group)) +
  geom_histogram(bins = 50) +
  scale_x_log10() + 
  ggtitle("Summary of price distributions") +
  facet_wrap(~room_type + neighbourhood_group)
```
```{r}
ggplot(airbnb, aes(availability_365, price)) +
  th +
  geom_point(alpha = 0.2, color = "slateblue") +
  geom_density(stat = "identity", alpha = 0.2) +
  xlab("Availability during year") +
  ylab("Price") +
  ggtitle("Relationship between availability",
          subtitle = "there is not clear relationship")
```
```{r}
ggplot(airbnb, aes(number_of_reviews, price)) +
  th + theme(axis.title = element_text(), axis.title.x = element_text()) +
  geom_point(aes(size = price), alpha = 0.05, color = "slateblue") +
  xlab("Number of reviews") +
  ylab("Price") +
  ggtitle("Relationship between number of reviews",
          subtitle = "The most expensive objects have small number of reviews (or 0)")
```

```{r}
airbnb %>% group_by(neighbourhood_group) %>% tally() %>% 
  ggplot(aes(x = reorder(neighbourhood_group, n), n)) +
  geom_bar(stat = "identity", fill = "purple") +
  theme_fivethirtyeight() +
  ggtitle("Number of objects by neighbourhood group") +
  geom_text(aes(x = neighbourhood_group, y = 1, label = paste0(n),
                colour = ifelse(neighbourhood_group %in%
                                                              c("Manhattan", "Brooklyn", 
                                                                "Queens"), '1', '2')),
            hjust=-1.5, vjust=.5, size = 4, 
            fontface = 'bold') +
  coord_flip() +
  scale_color_manual(values=c("white","black"), guide = F)
```

```{r}
airbnb <- airbnb %>% mutate(id = row_number())
airbnb_train <- airbnb %>% sample_frac(.7) %>% filter(price > 0)
airbnb_test  <- anti_join(airbnb, airbnb_train, by = 'id') %>% filter(price > 0)

# sanity check
nrow(airbnb_train) + nrow(airbnb_test) == nrow(airbnb %>% filter(price > 0))
```
```{r}
first_model <- train(price ~  room_type + minimum_nights  + availability_365 + neighbourhood_group, data = airbnb_train, method = "lm")
summary(first_model)
```
```{r}
plot(first_model$finalModel)
```
```{r}
airbnb$neighbourhood_group = fct_lump(f = airbnb$neighbourhood_group,prop = 0.1)
table(airbnb$neighbourhood_group)
```




#SECOND part of the Analysis

```{r, result = "hide"}
library(gbm)
library(xgboost)
library(lightgbm)
library(tidyverse)
library(ggthemes)
library(GGally)
library(ggExtra)
library(caret)
library(glmnet)
library(corrplot)
library(leaflet)
library(kableExtra)
library(RColorBrewer)
library(plotly)
```

```{r}
library(caTools)
library(caret)
library(tidyr);library(tidyverse);library(forecast);library(forcats)
data1 <- read.csv("C:/Users/josh1/Downloads/analysisData_ame.csv")
data1
scoring1 <- read.csv("C:/Users/josh1/Downloads/scoring_ame.csv")
glimpse(scoring1)
data2 <-data1 
scoring2 <- scoring1
```
Understanding the CLass of all the Variables
```{r}
sapply(data, class)

```

#IMPUTATION OF MISSING VARIABLES


```{r}

#imputation first

library(mice)
impD <- mice(data = data2, m =5, method = 'rf')
summary(impD)
data <- complete(impD,3)


library(mice)
impDsc <- mice(data = scoring2, m =5, method = 'rf')
summary(impDsc)
scoring <- complete(impDsc,3)
glimpse(scoring)
glimpse(data)
names(data)


#library(Amelia)
#missmap(data2)

```
## Removing the non numerical Columns to run the predictions
This was done espicially for the XGboost model because using the 
DATA filter method ran into a bug
```{r}
data = subset(data, select = -c(host_response_time,Ski.in.Ski.out,
                                host_response_rate,
                                zipcode_a,
                                neighbourhood_a,
                                Ceilinghoist,Kitchenette))


scoring1 = subset(scoring1, select = -c(host_response_time,Ski.in.Ski.out,
                                host_response_rate,
                                zipcode_a,
                                neighbourhood_a,
                                Ceilinghoist,Kitchenette))
```
## Using the Regression model 
though the method seem to give multi colinearity
the rmse generated through these predictors was 
lesser, just by using more numeric variables
```{r}
model = lm(price~
+host_total_listings_count
+room_type_a
+bathrooms
+beds
+monthly_price
+cleaning_fee
+maximum_nights
+maximum_minimum_nights
+maximum_maximum_nights
+maximum_nights_avg_ntm
+availability_60
+availability_365
+number_of_reviews_ltm
+last_review
+review_scores_accuracy
+review_scores_checkin
+review_scores_location
+calculated_host_listings_count
+calculated_host_listings_count_private_rooms
+reviews_per_month
+host_listings_count
+Air
+accommodates
+bedrooms
+square_feet
+weekly_price
+security_deposit
+guests_included
+minimum_nights
+minimum_minimum_nights
+minimum_maximum_nights
+minimum_nights_avg_ntm
+availability_30
+availability_90
+number_of_reviews
+first_review
+review_scores_rating
+review_scores_cleanliness
+review_scores_communication
+review_scores_value
+calculated_host_listings_count_entire_homes
+calculated_host_listings_count_shared_rooms
,data = firstrf)
summary(model)
pred = predict(model, newdata = firstrfsc)
pred
rmse5 = sqrt(mean((pred - data1$price)^2))
rmse5
```
## For furthering better results
there was more DATA wrangling required

```{r}
data = read.csv('C:/Users/josh1/Downloads/analysisData.csv')
scoring = read.csv('C:/Users/josh1/Downloads/scoringData.csv')
```

### The Data Structure

``` {r}
dim(data)
dim(scoring)
str(data)
```

```{r}
data$space = as.character(data$space)
data$host_verifications = as.character(data$host_verifications)
data$summary = as.character(data$summary)
data$description = as.character(data$description)
data$transit = as.character(data$transit)
data$host_about = as.character(data$host_about)
data$amenities = as.character(data$amenities)
data$neighborhood_overview = as.character(data$neighborhood_overview)
##PERFORM THE SAME FOR SCORING DATA
scoring$summary = as.character(scoring$summary)
scoring$amenities = as.character(scoring$amenities)
scoring$host_verifications = as.character(scoring$host_verifications)
scoring$transit = as.character(scoring$transit)
scoring$host_about = as.character(scoring$host_about)
scoring$description = as.character(scoring$description)

scoring$space = as.character(scoring$space)
scoring$neighborhood_overview = as.character(scoring$neighborhood_overview)
```

``` {r, results = "hide"}
library(ngram)
library(dplyr)
data = data %>%
  rowwise() %>%
  mutate(summary_wc = wordcount(summary),
         description_wc = wordcount(description),
         transit_wc = wordcount(transit),
         host_about_wc = wordcount(host_about),
         amenities_count = wordcount(amenities),
         space_wc = wordcount(space),
         neighborhood_overview_wc = wordcount(neighborhood_overview))
scoring = scoring %>%
  rowwise() %>%
  mutate(summary_wc = wordcount(summary),
         description_wc = wordcount(description),
         transit_wc = wordcount(transit),
         host_about_wc = wordcount(host_about),
         amenities_count = wordcount(amenities),
         space_wc = wordcount(space),
         neighborhood_overview_wc = wordcount(neighborhood_overview))
```

Based on my research and understanding, it was clear that I had to work with the Amenities column, so restructuring was converting 
Amenities into new columns for each creating 1's and 0's was the best option

``` {r}
## Removing Irrelevant signs from the columns
data$amenities = gsub("\\.", "", data$amenities)  ## remove the dot sign 
data$amenities = data$amenities %>% stringr::str_replace_all("\\s", "")   ## remove the space
data$amenities = noquote(data$amenities)   ##  remove quotation sign
## Second split the column and create dummy variables
data = cbind(data,mtabulate(strsplit(as.character(data$amenities), ',')))
## Check if it works
head(data$amenities, 3)
### we could also use colnames(data)
```



``` {r}
## First, remove other signs in the column like [, ], . 
data$host_verifications = gsub("\\[", "", data$host_verifications) 
data$host_verifications = gsub("\\]", "", data$host_verifications) 
data$host_verifications = gsub("\\'", "", data$host_verifications) 
data$host_verifications = data$host_verifications %>% stringr::str_replace_all("\\s", "") ## remove the space
data$host_verifications = noquote(data$host_verifications) ##  remove quotation sign
## Create dummy variables
data = cbind(data, mtabulate(strsplit(as.character(data$host_verifications), split = ','))) 
## calculate the wordcount for the text column chosen ###
data$host_identity_verified = as.character(data$host_identity_verified)
data = data %>%
    rowwise() %>%
    mutate(verification_count = wordcount(host_identity_verified))
## Check if it works
head(data$host_verifications, 3)
```


``` {r}
## First, remove other signs in the column like [, ], . 
data$host_verifications = gsub("\\[", "", data$host_verifications) 
data$host_verifications = gsub("\\]", "", data$host_verifications) 
data$host_verifications = gsub("\\'", "", data$host_verifications) 
data$host_verifications = data$host_verifications %>% stringr::str_replace_all("\\s", "") ## remove the space
data$host_verifications = noquote(data$host_verifications) ##  remove quotation sign
## Create dummy variables
data = cbind(data, mtabulate(strsplit(as.character(data$host_verifications), split = ','))) 
## calculate the wordcount for the text column chosen ###
data$host_identity_verified = as.character(data$host_identity_verified)
data = data %>%
    rowwise() %>%
    mutate(verification_count = wordcount(host_identity_verified))
## Check if it works
head(data$host_verifications, 3)
```

Finally, we do the same in scoring dataset.

``` {r, result = "hide"}
## First, the amenities column
scoring$amenities = gsub("\\.", "", scoring$amenities)  
scoring$amenities = scoring$amenities %>% stringr::str_replace_all("\\s", "")   
scoring$amenities = noquote(scoring$amenities)  
scoring = cbind(scoring,mtabulate(strsplit(as.character(scoring$amenities), ',')))
## Next this was done for the host_identifications column
scoring$host_verifications = gsub("\\[", "", scoring$host_verifications)
scoring$host_verifications = gsub("\\]", "", scoring$host_verifications)
scoring$host_verifications = gsub("\\'", "", scoring$host_verifications)
scoring$host_verifications = scoring$host_verifications %>% stringr::str_replace_all("\\s", "")
scoring$host_verifications = noquote(scoring$host_verifications)
scoring = cbind(scoring, mtabulate(strsplit(as.character(scoring$host_verifications), split = ',')))
scoring$host_identity_verified = as.character(scoring$host_identity_verified)
scoring = scoring %>%
    rowwise() %>%
    mutate(verification_count = wordcount(host_identity_verified))
```

Note Most Variables were had different spellings, which were changed

``` {r, result = "hide"}
colnames(data)[which(colnames(data) == '24-hourcheck-in')] = 'check_in_24'
colnames(data)[which(colnames(data) == 'Cat(s)')] = 'cat'
colnames(data)[which(colnames(data) == 'Dog(s)')] = 'dog'
colnames(data)[which(colnames(data) == 'Otherpet(s)')] = 'otherpet'
colnames(data)[which(colnames(data) == 'Washer/Dryer')] = 'Washer_and_Dryer'
colnames(data)[which(colnames(data) == 'Selfcheck-in')] = 'Selfcheck_in'
colnames(data)[which(colnames(data) == 'Family/kidfriendly')] = 'Family_and_kidfriendly'
colnames(scoring)[which(colnames(scoring) == '24-hourcheck-in')] = 'check_in_24'
colnames(scoring)[which(colnames(scoring) == 'Cat(s)')] = 'cat'
colnames(scoring)[which(colnames(scoring) == 'Dog(s)')] = 'dog'
colnames(scoring)[which(colnames(scoring) == 'Otherpet(s)')] = 'otherpet'
colnames(scoring)[which(colnames(scoring) == 'Washer/Dryer')] = 'Washer_and_Dryer'
colnames(scoring)[which(colnames(scoring) == 'Selfcheck-in')] = 'Selfcheck_in'
colnames(scoring)[which(colnames(scoring) == 'Family/kidfriendly')] = 'Family_and_kidfriendly'
```

Writing the new data to an excel just for verification purposes,
```{r}
write.csv(data, "C:/Users/josh1/Downloads/analysisData_ame.csv")
write.csv(scoring, "C:/Users/josh1/Downloads/scoring_ame.csv")

```

FInding Variables of Importance

```{r}
library(rpart)
library(rpart.plot)
tree2 = rpart(price~., data = data, method = 'anova')
tree2$variable.importance
```
## DROPING THESE Variables and running the code on multiple iterations gives shows us the rank order of the variables based on trees.


##RUNNING FOREST RANGER with 10000 trees still did not give me a very successful RMSE
```{r}
library(ranger)
set.seed(1031)
forest_ranger = ranger(price~.,
                       data = data, 
                       num.trees = 10000)


pred = predict(forest_ranger, data = scoring, num.trees = 10000)
rmse_forest_ranger = sqrt(mean((pred$predictions - data$price)^2)); rmse_forest_ranger
```
After Converting all DATA into to numeric values and runnin it though trees it still did
not give a good rmse
```{r}


library(rpart)
library(rpart.plot)
tree5 = rpart(price~.


     , data ,method = 'anova', control = rpart.control(cp=-0.01))
summary(tree5)
 pred6 = predict(tree5, newdata = scoring)
rmse_tree6 = sqrt(mean((pred6 - data$price)^2)); rmse_tree6

mean(pred6,na.rm = TRUE)
sum(is.na(pred6))
joy1 <- pred6
write.csv(joy1, "C:/Users/josh1/Downloads/submission_new_tree_joy1.csv")

submission3 = data.frame(id = scoring$id, pred6)
View(pred4)
mean(pred5$price ,na.rm = TRUE)

submission_file = write.csv(x= submission3,
                          file = 'C:/Users/josh1/Downloads/submission_new_joy1.csv' ,
                           row.names = F)

#mean(pred4,na.rm = TRUE)
#sum(is.na(pred4))
#View(pred4)
```

Using Specific Predictors after Analysis gave a much cleaner result
```{r}
library(rpart)
library(rpart.plot)
tree5 = rpart(price~room_type_a +calculated_host_listings_count_entire_homes + calculated_host_listings_count_private_rooms+  accommodates + cleaning_fee+bathrooms+weekly_price+neighbourhood_group_cleansed_price +bedrooms +  beds +  property_type_price  +guests_included + property_type_a + Freestreetparking + Elevator + Privateentrance  +  review_scores_location +host_listings_count+calculated_host_listings_count +  reviews_per_month + square_feet + Airconditioning + Dryer + Elevator + Family_and_kidfriendly + Freestreetparking + Hairdryer + Hangers + Iron + Laptopfriendlyworkspace + Kitchen+ Lockonbedroomdoor + Refrigerator + Shampoo+ Selfcheck_in + Stove  + TV + kba +jumio+first_review_a+last_review_a+room_type_a+calculated_host_listings_count_entire_homes+maximum_nights+maximum_minimum_nights+maximum_maximum_nights+maximum_nights_avg_ntm+availability_60+availability_365+number_of_reviews_ltm+last_review_a+review_scores_accuracy+review_scores_checkin+review_scores_location+calculated_host_listings_count+calculated_host_listings_count_private_rooms+reviews_per_month+host_listings_count+minimum_nights+minimum_minimum_nights+minimum_maximum_nights+minimum_nights_avg_ntm+availability_30+availability_90+number_of_reviews+first_review_a + selfie + Oven 
, data ,method = 'anova', control = rpart.control(cp=-0.01))

summary(tree5)
 pred3 = predict(tree3, newdata = scoring)
rmse_tree3 = sqrt(mean((pred3 - data$price)^2)); RMSE = 65.14476

                
                
#summary(tree5)
 pred6 = predict(tree5, data = scoring)
rmse_tree6 = sqrt(mean((pred6 - data$price)^2)); rmse_tree6
```
RMSE 56 on rstudio, and LEADERBOARD RMSE 65



